---
title: "circRNA filtering and testing"
output: html_document
---

#EIGHTH

##Prior to running this R markdown, you must run DCC on your samples to test for circular RNA. See https://github.com/dieterich-lab/DCC for instructions on how to perform this using Unix.

##I have also uploaded my own DCC log on the GitHub repository for this project.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("devtools")
require(devtools)
install.packages("remotes")
library("CircTest")
library("utils")
library("dplyr")
library("ggplot2")
```

# Make a list of your cell types and replicate numbers:
```{r}
singletypesprac <-  c("ASG","AVE","AVG","AWA","AWB","DD","PVD","VD")

singletypesprac_withreps <- c("ASG1", "ASG2", "ASG3", "ASG4", "AVE1", "AVE2", "AVE3", "AVG1", "AVG2", "AVG3", "AWA1", "AWA2", "AWA3", "AWA4", "AWB1", "AWB2", "AWB3", "AWB4", "AWB5", "DD1", "DD2", "DD3", "PVD1", "PVD2", "VD1", "VD2", "VD3", "VD4")
```

# Import of DCC output files into R:
```{r, include=FALSE}
setwd("D:/Zach Wolfe's CircRNA analysis") # set your working directory here

circRNA_table <- matrix(nrow = 28, ncol = 2, dimnames = list(x = singletypesprac_withreps, y = c(paste("circRNA count"), paste("Most frequently circularized gene"))))
circRNA_table[is.na(circRNA_table)] <- 0

CircRNACount_filtered_combined <- data.frame(matrix(ncol = 3, nrow = 0))
colnames <- c("Chr", "Start", "End")
colnames(CircRNACount_filtered_combined) <- colnames
CircRNACount_filtered_combined$Chr <- as.character()
CircRNACount_filtered_combined$Start <- as.numeric()
CircRNACount_filtered_combined$End <- as.numeric()

LinearCount_filtered_combined <- data.frame(matrix(ncol = 3, nrow = 0))
colnames <- c("Chr", "Start", "End")
colnames(LinearCount_filtered_combined) <- colnames
LinearCount_filtered_combined$Chr <- as.character()
LinearCount_filtered_combined$Start <- as.numeric()
LinearCount_filtered_combined$End <- as.numeric()

CircCoordinates_filtered_combined <- data.frame(matrix(ncol = 8, nrow = 0))
colnames <- c("Chr", "Start", "End", "Gene", "JunctionType", "Strand", "Start.End.Region", "OverallRegion")
colnames(CircCoordinates_filtered_combined) <- colnames
CircCoordinates_filtered_combined$Chr <- as.character()
CircCoordinates_filtered_combined$Start <- as.numeric()
CircCoordinates_filtered_combined$End <- as.numeric()
CircCoordinates_filtered_combined$Gene <- as.character()
CircCoordinates_filtered_combined$JunctionType <- as.numeric()
CircCoordinates_filtered_combined$Strand <- as.character()
CircCoordinates_filtered_combined$Start.End.Region <- as.character()
CircCoordinates_filtered_combined$OverallRegion <- as.character()

for (i in 1:length(singletypesprac_withreps)){
CircRNACount <- read.delim(paste0(singletypesprac_withreps[i], 'CircRNACount'))
LinearCount <- read.delim(paste0(singletypesprac_withreps[i], 'LinearCount'))
CircCoordinates <- read.delim(paste0(singletypesprac_withreps[i], 'CircCoordinates'))

CircRNACount_filtered <- Circ.filter(circ = CircRNACount,
                                     linear = LinearCount,
                                     Nreplicates = 1,
                                     filter.sample = 1,
                                     filter.count = 5,
                                     percentage = 0.1,
                                    )


CircCoordinates_filtered <- CircCoordinates[rownames(CircRNACount_filtered),]
LinearCount_filtered <- LinearCount[rownames(CircRNACount_filtered),]

# We need to combine chimeric.out.junctions columns, then put them on one big table

names(CircRNACount_filtered)[names(CircRNACount_filtered) == "Chimeric.out.junction"] <- paste0("Chimeric.out.junction", singletypesprac_withreps[i])
CircRNACount_filtered_combined <- full_join(CircRNACount_filtered_combined, CircRNACount_filtered)

names(LinearCount_filtered)[names(LinearCount_filtered) == "Chimeric.out.junction"] <- paste0("Chimeric.out.junction", singletypesprac_withreps[i])
LinearCount_filtered_combined <- full_join(LinearCount_filtered_combined, LinearCount_filtered)

CircCoordinates_filtered_combined <- full_join(CircCoordinates_filtered_combined, CircCoordinates_filtered)


circRNA_table[i,1] <- nrow(CircRNACount_filtered)

if (circRNA_table[i,1] != 0){
gene_count <- as.data.frame(table(CircCoordinates_filtered$Gene))
gene_count <- gene_count[rev(order(gene_count$Freq)),]
circRNA_table[i,2] <- as.character(first(gene_count$Var1))
 }
if (circRNA_table[i,1] == 0){
circRNA_table[i,2] <- as.character(paste("NA"))
 }
}

CircRNACount_filtered_combined[is.na(CircRNACount_filtered_combined)] <- 0
LinearCount_filtered_combined[is.na(LinearCount_filtered_combined)] <- 0
CircCoordinates_filtered_combined[is.na(CircCoordinates_filtered_combined)] <- 0
```

# Circular RNA test (Circ.test):
```{r}
test <- Circ.test(CircRNACount_filtered_combined,
                 LinearCount_filtered_combined,
                 CircCoordinates_filtered_combined,
                 group=c(rep(1,4), rep(2,3), rep(3,3), rep(4,4), rep(5,5), rep(6,3), rep(7,2), rep(8,4))
                 )
```

# Significant results are shown in a summary table:
```{r}
View(test$summary_table)

colnames(test$summary_table) <- c("Chr", "Start", "End", "Gene", "JunctionType", "Strand", "Start.End.Region", "OverallRegion", "sig_p", "ASG_ratio_mean", "AVE_ratio_mean", "AVG_ratio_mean", "AWA_ratio_mean", "AWB_ratio_mean", "DD_ratio_mean", "PVD_ratio_mean", "VD_ratio_mean")

for (j in rownames(test$summary_table)){
 Circ.ratioplot(CircRNACount_filtered_combined,
                LinearCount_filtered_combined,
                CircCoordinates_filtered_combined,
                plotrow = j,
                size = 15,
                groupindicator1 = c(rep("ASG",4), rep("AVE",3), rep("AVG",3), rep("AWA",4), rep("AWB",5), rep("DD",3), rep("PVD",2), rep("VD",4)),
                x = "Cell type",
                y = "Percentage of Circular RNA vs All RNA",
                gene_column = 4
                )
}
```
# Save your work:
```{r}
write.csv(test, file = "CircRNA test results.csv")
write.csv(test$summary_table, file = "CircRNA test results summary.csv")
write.csv(circRNA_table, file = "circRNA table.csv")
write.csv(CircRNACount_filtered_combined, file = "CircRNACount_filtered_combined.csv")
write.csv(LinearCount_filtered_combined, file = "LinearCount_filtered_combined.csv")
write.csv(CircCoordinates_filtered_combined, file = "CircCoordinates_filtered_combined.csv")
```

